\section*{SKILLS}
\begin{itemize}[leftmargin=0.7em, label={}, itemsep=0pt, parsep=0pt, topsep=0pt]
  \item \textbf{Languages:} Python (Pandas, Scikit-Learn, PyTorch), SQL (BigQuery, PostgreSQL, Snowflake), R, Bash, Excel
  \item \textbf{ML \& Statistics:} Time-Series Forecasting, Statistical Modeling, A/B Testing, XGBoost, LSTM, NLP
  \item \textbf{Cloud \& MLOps:} GCP (Vertex AI, BigQuery), AWS (S3), dbt, Apache Airflow, Docker, CI/CD, Git
\end{itemize}

\section*{EXPERIENCE}

\textbf{Data Science Intern} \hfill Jan 2025 -- Present \\
\textit{Nebraska Public Media} \hfill \textit{Lincoln, NE}
\begin{itemize}
  \item Developed time-series forecasting models (Prophet/ARIMA) to predict user engagement, improving business planning accuracy and identifying high-churn segments for Q3 strategy.
  \item Evaluated LLM prompt engineering performance for internal text summarization workflows, optimizing context extraction logic to reduce query latency by 20\%.
  \item Conducted exploratory data analysis on audio playback logs using SQL and Python, isolating structural drop-off intervals to improve listener retention metrics.
  \item Collaborated with engineering teams to implement automated data quality checks in BigQuery, ensuring reliable inputs for downstream statistical modeling.
\end{itemize}


\vspace{4pt}


\textbf{Data Science Intern} \hfill Jan 2024 -- Jan 2025 \\
\textit{Allo Communications} \hfill \textit{Lincoln, NE}
\begin{itemize}
  \item Built an end-to-end fraud detection pipeline using XGBoost, achieving 94\% precision in identifying fraudulent subscription patterns and protecting network revenue.
  \item Designed and executed A/B tests for customer engagement initiatives, utilizing power analysis to determine sample sizes and validate statistical significance of business decisions.
  \item Applied K-Means clustering and geospatial analysis to 1M+ network node logs, enabling the security team to reduce investigative cycles by 50\% through targeted anomaly detection.
\end{itemize}

\vspace{4pt}

\textbf{Machine Learning Research Assistant} \hfill Feb 2023 -- Jan 2024 \\
\textit{Nebraska Water Center} \hfill \textit{Lincoln, NE}
\begin{itemize}
  \item Trained multivariate LSTM architectures to forecast agricultural yield variations against historical climate trends, benchmarking performance against USDA ground-truth records.
  \item Developed predictive data models and interactive visualizations for crop growth patterns, contributing to co-authored research papers on agricultural yield forecasting.
  \item Consolidated 40+ years of fragmented environmental data into a centralized BigQuery warehouse, enabling large-scale historical trend analysis and feature engineering.
\end{itemize}

\section*{PROJECTS}
\begin{itemize}[leftmargin=0.7em, label={}, itemsep=2pt, parsep=0pt, topsep=2pt]
  \item \textbf{Agentic RAG Framework |} Built self-correcting search using LangGraph and Vertex AI. Enhanced retrieval relevance through hybrid BM25 and embedding search, effectively minimizing LLM hallucinations.
  \item \textbf{Customer Segmentation \& Retention |} Segmented user records into value tiers using K-Means clustering in Python and SQL. Identified high-risk churn segments to enable proactive retention strategies.
  \item \textbf{NLP Sentiment Analysis Engine |} Developed BERT pipeline to process large-scale reviews and map sentiment to revenue KPIs. Optimized PyTorch inference batching to significantly accelerate text processing.
\end{itemize}

\section*{EDUCATION}
\textbf{University of Nebraska-Lincoln} \hfill Graduated May 2026 \\
B.S. Computer Science and Data Science; Minor in Mathematics \hfill \textit{Lincoln, NE}

\section*{HONORS AND ACTIVITIES}
\begin{itemize}[leftmargin=0.7em, label={}, itemsep=1pt, parsep=0pt, topsep=2pt]
  \item \textbf{RaikesHacks:} Led a 4-person team to build a real-time event sync engine using Python and Firebase.
  \item \textbf{Dean's List:} Recognized for academic excellence at the University of Nebraska-Lincoln (2022--2026).
\end{itemize}